null_model

### 2020-09-14 analysis/ts_null_model.Rmd
Save out samples incrementally

  site_samples <- data.frame()
  for (j in 1:n){
    iter_samples <- data.frame()
    for(i in unique(plot_data$year)){
      year_data <- plot_data %>% filter(year == i)
      iter_samples <- rbind(iter_samples, get_samp_species(year_data))
    }
    site_samples <- rbind(site_samples, iter_samples %>% mutate(n = j))
  }
  site_samples %>%
    mutate(plot_id = filter_plot) %>%
    pivot_wider(names_from = samp_species, values_from = samp_abun)
}
```

@@

trait_data <- sample_plots %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, weight, 
            traitName, scientificName, plot_id, study_id)) %>%
  distinct()

sample_occurrence <- future_map(unique(sample_plots$plot_id), get_plot_sample, data = sample_plots, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)
pins::pin(sample_occurrence, board = "github")
sample_occurrence <- pins::pin_get("sample_occurrence", board = "github")

get_plot_FD <- function(traits, occ_df, filter_plot, ...) {
  plot_samples <- occ_df %>%
    filter(plot_id == filter_plot)

>>>>

  site_samples <- data.frame()
  for (j in 1:n){
    iter_samples <- data.frame()
    for(i in unique(plot_data$year)){
      year_data <- plot_data %>% filter(year == i)
      iter_samples <- rbind(iter_samples, get_samp_species(year_data))
    }
    site_samples <- rbind(site_samples, iter_samples %>% mutate(n = j))
  }
  plot_samples <- site_samples %>%
    mutate(plot_id = filter_plot) %>%
    pivot_wider(names_from = samp_species, values_from = samp_abun)

  save_dir <- here::here("data", "null_samples")
  fs::dir_create(save_dir)
  write.csv(plot_samples, paste0(save_dir, "/", filter_plot, "_samps.csv"))

  return(plot_samples)
}
```

@@

trait_data <- sample_plots %>% 
  select(-c(biotimeName, taxa, id_species, plot, year, weight, 
            traitName, scientificName, plot_id, study_id)) %>%
  distinct()
```

Get sample dataframe
```{r}
future::plan(multiprocess)
sample_occurrence <- future_map(unique(sample_plots$plot_id), get_plot_sample, data = sample_plots, n = n) %>%
  bind_rows() %>%
  replace(is.na(.), 0)

files <-  dir(here::here("data", "null_samples"), "*.csv")
sample_occurrence <- files %>%
  paste0(here::here("data", "null_samples"), "/", .) %>%
  map_dfr(~read_csv(.x) %>% mutate(plot_id = as.character(plot_id)) %>% replace(is.na(.), 0))

pins::pin(sample_occurrence, board = "github")
sample_occurrence <- pins::pin_get("sample_occurrence", board = "github")
```

```{r}
get_plot_FD <- function(traits, occ_df, filter_plot, ...) {
  plot_samples <- occ_df %>%
    filter(plot_id == filter_plot)
